A search for high-mass black holes in data from the second LIGO observing run using a Bayesian ranking-statistic

### 2021-04-15 main.tex
complete v2

\avi{
Talk about the differences in pastro calculation ~\cite{Farr:2015:PhRvD, Gaebel:2019:MNRAS,Galaudage:2020:PhRvD}
}

\greg{This needs more explanation and discussion. I know that in the Gaebel paper~\cite{Gaebel:2019:MNRAS}, they make the connection (they don't in FGMC~\cite{Farr:2015:PhRvD}). But, effectively the FAP is the p-value, the probability that the event arose from the background noise alone. Taking 1-FAP as identifying a real signal can be hugely problematic (Wikipedia has its own page on it \url{https://en.wikipedia.org/wiki/Misuse_of_p-values}). In this case, it is a reasonable thing to do, because you are saying "anything which rings up our detection statistic is astrophysical by virtue that it is coherent". But, that needs to be spelled out. Also, it may be useful to say that the p-astro calculated from, say, PyCBC/GSTLAL are not 1-FAP, but instead apply the FGMC population approach.}

@@

\begin{table}
    \centering
    \caption{
    Prior settings for the parameters used during our parameter estimation. The definitions of the parameters are documented in \citet{bilby_gwtc}~Table~E1.\label{tab:priors}}. The trigger time $t_c$ is obtained from the data products of \pycbc's O2 search.
    \begin{tabular}{c c c c}
    \hline
    Parameter & Shape & Limits \\
    \hline
          $\mathcal{M}/\msun$           & Uniform & 7--180  \\
          $q$                           & Uniform & 0.1--1  \\
          $M/\msun$                     & Constraint & 50--500  \\
          $d_\mathrm{L}/\mathrm{Mpc}$   & Comoving & 100--5000  \\
          $a_1$, $a_2$                  & Uniform & 0--1  \\
          $\theta_{JN}$                 & Sinusoidal & 0--$\pi$  \\
          $\psi$                        & Uniform & 0--$\pi$  \\
          $\phi$                        & Uniform & 0--$2\pi$  \\
          ra                            & Uniform & 0--$2\pi$  \\
          dec                           & Cosine & 0--$2\pi$  \\
          $t_c/\mathrm{s}$              & Uniform & $t_c\pm0.1$  \\
    \hline
    \end{tabular}
\end{table}

@@

\subsection{New Candidate Events}
Although no clear detections are made with the \bcr, a marginal-candidate 170222 has been discovered with a $\pastrobcr\sim0.5$. This candidate has an SNR$\sim7.7$, low spin magnitudes and source-frame component masses of ${47.16}_{-5.77}^{+8.00}, {35.50}_{-6.35}^{+5.79}$, making it one of the heavier black-hole mergers from O2 and \GWTC. This candidate may be of interest as one component black hole may lie in the pair-instability mass gap ($55^{+10}_{-10}-148^{+13}_{-12}\msun$)~\cite{Woosley:2021:arXiv, Heger:2002:ApJ}. More details on the candidate are presented in Appendix~\ref{apdx:170222}. The remaining coherent trigger candidates all have $\pastrobcr\ll0.5$ making them unlikely to originate from astrophysical sources.

@@

\greg{If the search is better at identifying high-mass black holes and has not found any.. doesn't this mean we can better constraint their population properties? Do we know how much (if at all) this method outperforms current searches? This question may be stretching the scope of the paper, but I wondered if you had some thoughts.}

\avi{
\begin{itemize}
    \item Unlike for stellar-mass BBH, there are still alot of uncertainties for IMBH formation scenarios. Hence, upper limits would be challenging to calculate
    \item We would require to do more robust simulation studies to see what would fall in/outside our detection threshold, to put constraints on population properties and study the search's sensitivity
\end{itemize}
}

@@

\section{A closer look at 170222}\label{apdx:170222}
PyCBC found in chunk7, with template, corresponds to parameters Xyz. Our parameters state that it is xyz.
Put in corner, write notes from

>>>>

\avi{
The pastro calculation may need some more discussion. Taking pastro = 1-FAP as identifying a real signal can be hugely problematic: \url{https://en.wikipedia.org/wiki/Misuse_of_p-values}, even though its ok in this case. Maybe the following papers have something that can help motivate this ~\cite{Farr:2015:PhRvD, Gaebel:2019:MNRAS,Galaudage:2020:PhRvD}
}

@@

\begin{table}
    \centering
    \caption{
    Prior settings for the parameters used during our parameter estimation. The definitions of the parameters are documented in \citet{bilby_gwtc}~Table~E1. The trigger time $t_c$ is obtained from the data products of \pycbc's O2 search. \label{tab:priors}} 
    \begin{tabular}{c c c c}
    \hline
    Parameter & Shape & Limits \\
    \hline
          $\mathcal{M}/\msun$           & Uniform & 7--180  \\
          $q$                           & Uniform & 0.1--1  \\
          $M/\msun$                     & Constraint & 50--500  \\
          $d_\mathrm{L}/\mathrm{Mpc}$   & Comoving & 100--5000  \\
          $a_1$, $a_2$                  & Uniform & 0--1  \\
          $\theta_{JN}$                 & Sinusoidal & 0--$\pi$  \\
          $\psi$                        & Uniform & 0--$\pi$  \\
          $\phi$                        & Uniform & 0--$2\pi$  \\
          ra                            & Uniform & 0--$2\pi$  \\
          dec                           & Cosine & 0--$2\pi$  \\
          $t_c/\mathrm{s}$              & Uniform & $t_c\pm0.1$  \\
    \hline
    \end{tabular}
\end{table}

@@

\subsection{New Candidate Events}
Although no clear detections are made with the \bcr, a marginal-candidate 170222 has been discovered with a $\pastrobcr\sim0.5$. This candidate has an SNR$\sim7.7$, low spin magnitudes and source-frame component masses of $({47.16}_{-5.77}^{+8.00}, {35.50}_{-6.35}^{+5.79}) \msun$, making it one of the heavier black-hole mergers from O2 and \GWTC. This candidate may be of interest as one component black hole may lie in the pair-instability mass gap ($55^{+10}_{-10}-148^{+13}_{-12}\msun$)~\cite{Woosley:2021:arXiv, Heger:2002:ApJ}. More details on the candidate are presented in Appendix~\ref{apdx:170222}. The remaining coherent trigger candidates all have $\pastrobcr\ll0.5$ making them unlikely to originate from astrophysical sources.

@@

\greg{can we better constraint their population properties? Do we know how much (if at all) this method outperforms current searches?}

\avi{Unlike for stellar-mass BBH, there are still alot of uncertainties for IMBH formation scenarios. Hence, upper limits would be challenging to calculate. Additionally, we would require to do more robust simulation studies to see what would fall in/outside our detection threshold, to put constraints on population properties and study the search's sensitivity
}

@@

\section{A closer look at 170222}\label{apdx:170222}
PyCBC found the candidate 170222 with $\mathcal{M}_c=49.46$ and $q=0.68$, values that fall within our uncertainty limits. Some of the posteriors that were produced as a by-product of our \bcr calculation can be viewed in Fig.~\ref{fig:170222}.

\begin{figure*}
    \centering
    \begin{subfigure}
        \centering
        \includegraphics[width=0.45\linewidth]{170222_prior_posterior.png}
    \end{subfigure}
    ~ 
    \begin{subfigure}
        \centering
        \includegraphics[width=0.45\linewidth]{170222_source_posterior.png}
    \end{subfigure}
    \caption{Posterior distributions for some parameters of 170222, comparing posteriors in orange and prior probability density functions to the one-dimensional marginal distributions in green. 
    Left: Posterior probability distributions for 4 of the 11 search parameters. Sections of the prior probability density functions used for analysis are displayed in green in one-dimensional marginal distributions plots.
    Right: Posterior probability distributions for some inferred parameters.
    \label{fig:170222}}
\end{figure*}
